---
title: "Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## Topic 1

```{r check}
getwd()

file.exists("nips4b_birds_testfile0006.wav")

file.exists("../../audio/nips4b_birds_testfile0006.wav")
dir("../../audio")

dir("C:/Users/ggc34/OneDrive - University of Keele/Documents/Keele_academic/data/test_audio")
wav_fp <- "C:/Users/ggc34/OneDrive - University of Keele/Documents/Keele_academic/data/test_audio/nips4b_birds_testfile0006.wav"
file.exists(wav_fp)

```


### Exercise 

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r two-plus-two, exercise=TRUE}

```


```{r, echo=FALSE}
textInput("dataFolder", "data", value = "", width = NULL, placeholder = NULL)
sliderInput("bins", "Number of bins:", min = 1, max = 50, value = 30)
plotOutput("distPlot")

verbatimTextOutput("dataFolder")

tags$audio(src = "nips4b_birds_testfile0006.wav", type = "audio/wav", autoplay = NA, controls = NA)
#tags$audio(src = wav_fp, type = "audio/wav", autoplay = NA, controls = NA)

```

```{r, context="server"}
output$distPlot <- renderPlot({
  x <- faithful[, 2]  # Old Faithful Geyser data
  bins <- seq(min(x), max(x), length.out = input$bins + 1)
  hist(x, breaks = bins, col = 'darkgray', border = 'white')
  
})

output$dataFolder <- renderText({input$dataFolder})

```


### Quiz

```
# tags$audio(src = "audio/nips4b_birds_testfile0006.wav", type = "audio/wav", autoplay = NA, controls = NA)
```

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

